### 2018-09-11 Chapters/Chapter3.tex
commit

We start by considering only the exchange interaction part. Consider the Hamiltonian:

@@

Which is the Hamiltonian \ref{Hubbard} without DMI interaction. We can introduce a time dependent electric field in this Hamiltonian by adding a phase to the hopping term $t_{ij}(t) = t_0e^{ieaA_{ij}(t)}$, where $A_{ij}$ is the projection of the vector potential into the vector from site $i$ to $j$. The electric field has the form $\bs{E}(t) = E_0 (\sin (\omega t) \hat{e}_x + \lambda \cos (\omega t)\hat{e}_y)$ where $\lambda = 0, \pm 1$ representing planar or circular polarized field. We can therefore take $A_{ij} = \frac{E_0}{\omega} (-\cos(\omega t)\hat{e}_x +  \lambda \sin(\omega t)\hat{e}_y)\hat{e}_{ij}$, where $\hat{e}_{ij}$ is a unit vector pointing from site $i$ to site $j$.

@@

\begin{equation}
H_{m,ij} = \begin{cases}
	\frac{t_0}{T} \int_0^T dt e^{i\omega mt} e^{\mp iea\frac{E_0}{\omega}\cos(\omega t)}, & \text{for } \hat{e}_{ij} = \pm \hat{x} \\
	\frac{t_0}{T} \int_0^T dt e^{i\omega mt} e^{\pm iea\lambda\frac{E_0}{\omega}\sin(\omega t)}, & \text{for } \hat{e}_{ij} = \pm \hat{y} \\
\end{cases} \quad
\end{equation}

>>>>

We start by considering only the exchange interaction part in a one-dimensional lattice. Consider the Hamiltonian:

@@

Which is the Hamiltonian \ref{Hubbard} without DMI interaction. We can introduce a time dependent electric field in this Hamiltonian by adding a phase to the hopping term $t_{ij}(t) = t_0e^{ieaA_{ij}(t)}$, where $A_{ij}$ is the projection of the vector potential into the vector from site $i$ to $j$. The electric field has the form $\bs{E}(t) = E_0 \sin (\omega t)$ (one-dimensional lattice). We can therefore take $A_{ij} = -\frac{E_0}{\omega}\cos(\omega t)(i-j)$.

@@

\begin{equation}
H_{m} = \frac{t_0}{T} \sum_{\langle i,j \rangle, \sigma} \int_0^T dt e^{i\omega mt} e^{-iea\frac{E_0}{\omega}\cos(\omega t)(i-j)}\hat{c}_{i\sigma}^\dagger \hat{c}_{j\sigma} = -t_0 \sum_{\langle i,j \rangle, \sigma} (-1)^mJ_m((i-j)ea\frac{E_0}{\omega})\hat{c}_{i\sigma}^\dagger \hat{c}_{j\sigma}
\end{equation}

Where $J_m(x)$ is the \textit{m}th Bessel function.
